Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
minor things to improve layout

\begin{figure}[tb]
  \centering
  \includegraphics[width=1\columnwidth] {images/success-rates-large}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.3cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/success-rates-tiny}
    \caption{Success rates on the memory-constrained cluster. Higher is better. }
%        by algorithm by workflow size.
    \label{fig:success-rates-tiny}
    \vspace{-0.3cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.3cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-constrained-onlyvalid}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
    \vspace{-0.3cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
    \caption{Running times of the heuristics. The y axis is logarithmic.}
    \label{fig:runtimes-log}
    \vspace{-0.3cm}
\end{figure}

@@

We have formalized a scheduling problem in memory-constrained environments, where tasks
may exceed the memory available on a processor and resort to communication buffers
to store and communicate data between processors. In this context, we have 
designed three memory-aware HEFT-based heuristics, which account for memory
constraints while scheduling tasks.

Two heuristics rely on an ordering of tasks based on the bottom level of tasks, with the objective
of minimizing the makespan and hence scheduling critical tasks first. The third one, \heftmm,
goes one step further and handles tasks in an order dictated by an efficient traversal
of the graph in terms of memory requirements, hence reducing the memory used
by the schedule. Experimental results on a large set of workflows coming from real-life applications
demonstrate that the memory-aware heuristics produce valid schedules successfully. 
In the most memory-constrained setting, \heftmm succeeds to schedule even the largest workflows,
while the other heuristics return invalid schedules that exceed the memory capacity. 
This advantage of \heftmm comes at the price of worse makespans than with \heftbl
and \heftblc. % which focus on makespan by ordering tasks by bottom level. 
As expected, the baseline \heft, which is not memory-aware, returns invalid schedules in almost
all settings, except for very small workflows.

@@

This work could be extended in several directions. First, the model could be refined to include
heterogeneous bandwidths, while we consider a homogeneous communication network. 
More importantly, it would be interesting to consider other types of variability, for instance
if new tasks appear in (or disappear from) the workflow graph, or if there is variability in the platform, 
with processors arriving and departing. We believe that we could adapt the current approach
by recomputing schedules on the fly, and we plan to perform a new set of experiments
to further assess the impact of dynamic scheduling.

%
%\begin{itemize}
%  \item Extend to heterogeneous bandwidths. 
%  \item Further variability commented out from the paper: changing DAG structure; changing platform...
%\end{itemize}

\balance
    \bibliographystyle{abbrv}%IEEEtran}
    \bibliography{references}

>>>>

\begin{figure}[tb]
  \centering
  \includegraphics[width=1\columnwidth] {images/success-rates-large}
  \caption{Success rates on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
  \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/success-rates-tiny}
    \caption{Success rates on the memory-constrained cluster. Higher is better. }
%        by algorithm by workflow size.
    \label{fig:success-rates-tiny}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size-constrained}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/mem-usage-constrained-onlyvalid}
    \caption{Memory usage on the memory-constrained  cluster. } % by different heuristics by workflow size.}
    \label{fig:memory-usage-constrained}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
    \caption{Average running times (in seconds) of the heuristics \wrt workflow size. The $y$-axis is logarithmic.}
    \label{fig:runtimes-log}
    \vspace{-0.3cm}
\end{figure}

@@

We have formalized a scheduling problem in memory-constrained environments where tasks
may exceed the memory available on a processor and resort to communication buffers
to store and communicate data between processors. In this context, we have 
designed three memory-aware HEFT-based heuristics which account for memory
constraints when scheduling workflow tasks.

Two of these heuristics rely on a task ordering \wrt the bottom level of tasks, with the objective
of minimizing the makespan and hence scheduling critical tasks first. The third one, \heftmm,
% goes one step further and 
handles tasks in an order dictated by an efficient traversal
of the workflow in terms of memory requirements, hence reducing the memory used
by the schedule. Experimental results on a large set of workflows from real-world applications
demonstrate that the memory-aware heuristics produce valid schedules successfully. 
In the most memory-constrained setting, \heftmm succeeds to schedule even the largest workflows,
while the other heuristics return invalid schedules that exceed the memory capacity. 
This advantage of \heftmm comes at the price of worse makespans than those of \heftbl
and \heftblc. % which focus on makespan by ordering tasks by bottom level. 
As expected, the baseline \heft, which is not memory-aware, returns invalid schedules in almost
all cases, except for very small workflows.

@@

This work can be extended in several directions. First, the model could be refined to include
heterogeneous bandwidths. %, while we consider a homogeneous communication network. 
More importantly, it would be interesting to consider other types of variability, \egc
if new tasks (dis)appear in the workflow graph, or if there is variability in the platform, 
with processors arriving and departing. We believe that we could adapt the current approach
based on recomputing schedules on the fly, and we plan to perform a new set of experiments
to further assess the impact of dynamic scheduling techniques.

%
\balance
    \bibliographystyle{abbrv}%IEEEtran}
    \bibliography{references}
